\begin{thebibliography}{99}

% IEEE and Journal Papers on Monitoring and Resource Management
\bibitem{distributed_monitoring}
M. L. Massie, B. N. Chun, and D. E. Culler, ``The Ganglia distributed monitoring system: design, implementation, and experience,'' \textit{Parallel Computing}, vol. 30, no. 7, pp. 817-840, July 2004.

\bibitem{network_monitoring}
B. Claise, ``Cisco Systems NetFlow Services Export Version 9,'' RFC 3954, Internet Engineering Task Force (IETF), October 2004.

\bibitem{performance_monitoring}
P. Barham, A. Donnelly, R. Isaacs, and R. Mortier, ``Using Magpie for request extraction and workload modelling,'' in \textit{Proc. 6th USENIX Symposium on Operating Systems Design and Implementation (OSDI)}, San Francisco, CA, USA, 2004, pp. 259-272.

\bibitem{capacity_planning}
D. Gmach, J. Rolia, L. Cherkasova, and A. Kemper, ``Capacity management and demand prediction for next generation data centers,'' in \textit{Proc. IEEE International Conference on Web Services (ICWS)}, Salt Lake City, UT, USA, 2007, pp. 43-50.

\bibitem{bottleneck_detection}
P. Bodik, M. Goldszmidt, A. Fox, D. B. Woodard, and H. Andersen, ``Fingerprinting the datacenter: automated classification of performance crises,'' in \textit{Proc. 5th European Conference on Computer Systems (EuroSys)}, Paris, France, 2010, pp. 111-124.

\bibitem{anomaly_detection}
V. Chandola, A. Banerjee, and V. Kumar, ``Anomaly detection: A survey,'' \textit{ACM Computing Surveys}, vol. 41, no. 3, Article 15, pp. 1-58, July 2009.

\bibitem{resource_optimization}
J. O. Kephart and D. M. Chess, ``The vision of autonomic computing,'' \textit{IEEE Computer}, vol. 36, no. 1, pp. 41-50, January 2003.

\bibitem{energy_efficiency}
A. Beloglazov and R. Buyya, ``Energy efficient resource management in virtualized cloud data centers,'' in \textit{Proc. 10th IEEE/ACM International Conference on Cluster, Cloud and Grid Computing (CCGrid)}, Melbourne, Australia, 2010, pp. 826-831.

\bibitem{alert_systems}
S. Kandula, R. Mahajan, P. Verkaik, S. Agarwal, J. Padhye, and P. Bahl, ``Detailed diagnosis in enterprise networks,'' \textit{ACM SIGCOMM Computer Communication Review}, vol. 39, no. 4, pp. 243-254, October 2009.

\bibitem{agentless_monitoring}
R. H. Arpaci-Dusseau and A. C. Arpaci-Dusseau, ``Operating Systems: Three Easy Pieces,'' Arpaci-Dusseau Books, Chapter 36: I/O Devices, 2018.

% Time-Series Databases and Data Management
\bibitem{tsdb_survey}
A. Bader, O. Kopp, and M. Falkenthal, ``Survey and Comparison of Open Source Time Series Databases,'' in \textit{Proc. Conference on Database Systems for Business, Technology, and Web (BTW)}, Stuttgart, Germany, 2017, pp. 249-268.

\bibitem{data_compression}
P. A. Boncz, M. L. Kersten, and S. Manegold, ``Breaking the memory wall in MonetDB,'' \textit{Communications of the ACM}, vol. 51, no. 12, pp. 77-85, December 2008.

\bibitem{columnar_storage}
D. J. Abadi, S. R. Madden, and N. Hachem, ``Column-stores vs. row-stores: how different are they really?'' in \textit{Proc. ACM SIGMOD International Conference on Management of Data}, Vancouver, Canada, 2008, pp. 967-980.

\bibitem{query_optimization}
M. Stonebraker and U. Cetintemel, ``One size fits all: an idea whose time has come and gone,'' in \textit{Proc. 21st International Conference on Data Engineering (ICDE)}, Tokyo, Japan, 2005, pp. 2-11.

\bibitem{indexing_techniques}
G. Graefe, ``Modern B-Tree Techniques,'' \textit{Foundations and Trends in Databases}, vol. 3, no. 4, pp. 203-402, 2011.

\bibitem{database_performance}
A. Pavlo and M. Aslett, ``What's Really New with NewSQL?'' \textit{SIGMOD Record}, vol. 45, no. 2, pp. 45-55, September 2016.

% Network Protocols and Security
\bibitem{ssh_protocol}
T. Ylonen and C. Lonvick, ``The Secure Shell (SSH) Protocol Architecture,'' RFC 4251, Internet Engineering Task Force (IETF), January 2006.

\bibitem{snmp}
J. Case, M. Fedor, M. Schoffstall, and J. Davin, ``Simple Network Management Protocol (SNMP),'' RFC 1157, Internet Engineering Task Force (IETF), May 1990.

\bibitem{network_security}
W. Stallings, ``Network Security Essentials: Applications and Standards,'' 6th edition, Pearson, 2017.

\bibitem{encryption}
B. Schneier, ``Applied Cryptography: Protocols, Algorithms, and Source Code in C,'' 2nd edition, John Wiley \& Sons, 1996.

% Web Technologies and APIs
\bibitem{rest_architecture}
R. T. Fielding, ``Architectural Styles and the Design of Network-based Software Architectures,'' Doctoral dissertation, University of California, Irvine, 2000.

\bibitem{web_api_design}
L. Richardson and S. Ruby, ``RESTful Web Services,'' O'Reilly Media, 2007.

\bibitem{spa_frameworks}
A. Freeman, ``Pro React 16,'' Apress, 2019.

% Visualization and User Interface
\bibitem{visualization}
B. Shneiderman, ``The eyes have it: A task by data type taxonomy for information visualizations,'' in \textit{Proc. IEEE Symposium on Visual Languages}, Boulder, CO, USA, 1996, pp. 336-343.

\bibitem{dashboard_design}
S. Few, ``Information Dashboard Design: Displaying data for at-a-glance monitoring,'' 2nd edition, Analytics Press, 2013.

% Tools and Technologies Documentation
\bibitem{timescaledb}
Timescale, Inc., ``TimescaleDB Documentation - An open-source time-series SQL database,'' 2024. \\
Available: \url{https://docs.timescale.com/}

\bibitem{postgresql}
PostgreSQL Global Development Group, ``PostgreSQL 18 Documentation,'' 2024. \\
Available: \url{https://www.postgresql.org/docs/18/}

\bibitem{nodejs}
OpenJS Foundation, ``Node.js Documentation,'' 2024. \\
Available: \url{https://nodejs.org/docs/}

\bibitem{react}
Meta Platforms, Inc., ``React Documentation - A JavaScript library for building user interfaces,'' 2024. \\
Available: \url{https://react.dev/}

\bibitem{nmap}
G. Lyon, ``Nmap Network Scanning: The Official Nmap Project Guide,'' Insecure.Com LLC, 2024. \\
Available: \url{https://nmap.org/book/}

\end{thebibliography}
